Communicating causal effect heterogeneity

### 2024-09-03 index.qmd
Re-render site

# Packages
library(janitor)
library(scales)
library(ellipse)
library(tinytable)
library(cmdstanr)
library(readxl)
library(lme4)
library(ggpp)
library(patchwork)
library(latex2exp)
library(ggdist)
library(ggstance)
library(tidybayes)
library(distributional)
library(posterior)
library(parameters)
library(brms)
library(tidyverse)
library(knitr)

@@

# Model estimation options, customize in .Renviron
dir.create("models", FALSE)
options(
  brms.backend = Sys.getenv("BRMS_BACKEND", "rstan"), 
  brms.threads = as.numeric(Sys.getenv("MAX_CORES"), 1),
  mc.cores = as.numeric(Sys.getenv("MAX_CORES"), 4)
)
```

@@

fit_1 <- brm(
  rt ~ 1 + valence + (1 + valence | person),
  data = dat,
  file = "models/brm-fit-1",
  control = list(adapt_delta = .95)
)

@@

@@

```{r}
#| label: fig-2-target
#| fig-height: 4
#| fig-width: 7.4
#| fig-cap: "Heterogeneity between target words in memory performance in Free recall and Cued recall tasks from Model 2. **A**. Histograms of 4,000 posterior draws from the model parameters and their transformations, with points and intervals showing posterior means and 95\\%CIs. Differences calculated as Cued - Free recall. **B**. Probability density (top) and cumulative distribution functions (bottom) of the two tasks' heterogeneity distributions (green: free recall, red: cued recall). The densities, points, and intervals on the left y-axis of the bottom panel indicate approximate posterior densities, with means and 95\\%CIs, of the proportions of the populations with memory performance above chance. Densities, points, and intervals on the x-axis of the bottom panel indicate approximate posterior densities, with means and 95%CIs, of the 90\\% heterogeneity interval's lower (left) and upper (right) bounds. **C**. Posterior mean (dark), and 100 posterior draws (light) of the correlation between target words' proportions correct in the free (x-axis) and cued recall (y-axis) tasks. Ellipses indicate the 90th percentile of the bivariate normal distribution. Small black circles are estimated parameters for target words in the sample (posterior means of $\\gamma$)."

@@

<!-- HTML format automatically adds "References" in an appendix. -->
::: {.content-hidden when-format="html"}
# References

>>>>

# Packages
library(janitor)
library(scales)
library(ellipse)
library(cmdstanr)
library(readxl)
library(lme4)
library(ggpp)
library(patchwork)
library(latex2exp)
library(ggdist)
library(ggstance)
library(tidybayes)
library(distributional)
library(posterior)
library(parameters)
library(brms)
library(tidyverse)
library(knitr)

@@

# Model estimation options, customize in .Renviron
dir.create("models", FALSE)
options(
  brms.backend = Sys.getenv("BRMS_BACKEND", "rstan"), 
  brms.threads = as.numeric(Sys.getenv("BRMS_THREADS"), 1),
  mc.cores = as.numeric(Sys.getenv("MAX_CORES"), 4)
)
```

@@

fit_1 <- brm(
  rt ~ 1 + valence + (1 + valence | person),
  data = dat,
  file = "models/brm-fit-1",
)

@@

```{r include = is_html}
post1 |> 
  head() |> 
  as_tibble() |> 
  select(-contains(".")) |> 
  select(2, 4, 7) |> 
  mutate(
    hi90 = str_glue(
      "[{number(quantile(dist_valence, .05), .01)}, ",
      "{number(quantile(dist_valence, .95), .01)}]"
      ),
    pp = cdf(dist_valence, 0),
    prope = cdf(dist_valence, .1) - cdf(dist_valence, -.1),
    ratio = sd_person__valence1 / b_valence1
  ) |> 
  mutate(dist_valence = as.character(dist_valence)) |> 
  # setNames(c(m1_parnames, "$p(\\beta_1)$")) |> 
  setNames(
    c(
      m1_parnames[c(2, 4)], 
      "$p(\\beta_1)$", "$HI_{90}$", "$p^+$", "$p^{ROPE}$", "$\\frac{\\tau_1}{\\beta_1}$"
    )
  ) |> 
  kable(digits = 2)
```

@@

```{r}
#| label: fig-2-target
#| fig-height: 3.6
#| fig-width: 7.4
#| fig-cap: "Heterogeneity between target words in memory performance in Free recall and Cued recall tasks from Model 2. **A**. Histograms of 4,000 posterior draws from the model parameters and their transformations, with points and intervals showing posterior means and 95\\%CIs. Differences calculated as Cued - Free recall. **B**. Probability density (top) and cumulative distribution functions (bottom) of the two tasks' heterogeneity distributions (green: free recall, red: cued recall). The densities, points, and intervals on the left y-axis of the bottom panel indicate approximate posterior densities, with means and 95\\%CIs, of the proportions of the populations with memory performance above chance. Densities, points, and intervals on the x-axis of the bottom panel indicate approximate posterior densities, with means and 95%CIs, of the 90\\% heterogeneity interval's lower (left) and upper (right) bounds. **C**. Posterior mean (dark), and 100 posterior draws (light) of the correlation between target words' proportions correct in the free (x-axis) and cued recall (y-axis) tasks. Ellipses indicate the 90th percentile of the bivariate normal distribution. Small black circles are estimated parameters for target words in the sample (posterior means of $\\gamma$)."

@@

<!-- HTML format automatically adds "References" in an appendix. -->
::: {.content-hidden when-format="html"}
# References {.unnumbered}
